Let's talk about Thurstone \& Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2024-11-30 _tex/index.tex
Built site for gh-pages

Nevertheless, despite the increasing number of CJ studies, unsystematic
and fragmented research approaches have left several critical issues
unaddressed. The present study primarily focuses on three: the
over-reliance on the assumptions of Thurstone's Case V in the
statistical analysis of CJ data, the apparent disconnect between CJ's
trait measurement and hypothesis testing, and the unclear role of the
diverse assessment design features on CJ's reliability and validity. The
following sections begin with a brief overview of Thurstone's theory and
a detailed discussion of these issues. Subsequently, the study
introduces a theoretical model for CJ that builds upon Thurstone's
theory, alongside its statistical translation, designed to address all
three concerns simultaneously.

@@

In its most general form, Thurstone's theory
\citeyearpar{Thurstone_1927b} suggests that two factors determine the
dichotomous outcome of pairwise comparisons: the discriminal process of
each stimulus and their discriminal difference. The \emph{discriminal
process} refers to the psychological effect each stimulus exerts on the
judges, or more simply, the underlying perception of the stimulus' trait
level. According to the theory, the discriminal process for each
stimulus follows a Normal distribution. The mode (mean) of this
distribution, referred to as the \emph{modal discriminal process},
represents the stimulus' position on the trait continuum. Meanwhile, the
dispersion of the distribution, referred to as the \emph{discriminal
dispersion}, reflects the variability in the perceived trait level of
the stimulus.

Nevertheless, the theory posits that because the discriminal process of
a single stimulus is not directly observable, the \emph{law of
comparative judgment} becomes essential. This law states that in
pairwise comparisons, the stimulus positioned further along the trait
continuum is perceived as having a higher level of that trait. This
emphasize that the outcome depends on the relative distance between
stimuli, rather than their absolute positions on the trait continuum.
Thus, the theory assumes the observed dichotomous outcome is determined
by the distribution of the difference between the underlying discriminal
processes of the stimuli, referred to as the \emph{discriminal
difference}.

These concepts are more easily understood through an example. For
instance, in the context of evaluating text quality,
Figure~\ref{fig-discriminal_process} depicts the underlying discriminal
process distributions for two written texts. The figure highlights
differences in the texts' positions along the quality trait continuum,
represented by their modal discriminal processes, as well as differences
in the variability of their perceived trait levels, represented by their
discriminal dispersions. Furthermore,
Figure~\ref{fig-discriminal_difference} displays the discriminal
difference distribution for these texts. This figure shows that text A
is perceived to exhibit significantly higher quality than text B, as
indicated by the shaded gray area. Consequently, the dichotomous outcome
of this comparison would likely favor text A.

@@

\begin{minipage}{0.50\linewidth}

@@

\includegraphics[width=0.95\linewidth,height=\textheight,keepaspectratio]{./images/figures/discriminal_process.png}

@@

\subcaption{\label{fig-discriminal_process}Discriminal processes}

\end{minipage}%
%
\begin{minipage}{0.50\linewidth}

@@

\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./images/figures/comparative_judgment.png}

@@

\subcaption{\label{fig-discriminal_difference}Discriminal difference}

\caption{\label{fig-thurstone_theory}Example distribution of discriminal
processes and their discriminal difference for two written texts
(stimuli or objects). Extracted from \citet[pp.~249-251]{Bramley_2008}.}

@@

Importantly, the general form of Thurstone's theory primarily addressed
pairwise comparisons of stimuli made by a single judge
\citep[pp.~267]{Thurstone_1927b}. Thus, to facilitate its practical
application, Thurstone developed five distinct cases derived from this
general form. Each case progressively introduces additional simplifying
assumptions related to different features of the theory, such as the
distribution of discriminal processes, the uniformity of discriminal
dispersions across stimuli, the correlation between stimuli, and the
number of judges performing the comparisons. A summary of these cases is
provided in Table~\ref{tbl-thurstone_cases}. For a detailed examination
of this progression, refer to \citet{Thurstone_1927b} and
\citet[pp.~248-253]{Bramley_2008}.

@@

Despite its reliance on the largest number of simplifying assumptions
\citetext{\citealp[pp.~253]{Bramley_2008}; \citealp[pp.~677]{Kelly_et_al_2022}},
Case V remains the most widely used case in the CJ literature. This
popularity is largely due to its simplified statistical representation
in the Bradley-Terry-Luce (BTL) model
\citep{Bradley_et_al_1952, Luce_1959}. The BTL model mirrors the
assumptions of Case V, with one key difference: while Case V assumes a
Normal distribution for the discriminal processes of the stimuli, the
BTL model uses the more mathematically tractable Logistic distribution
\citep[pp.~254]{Andrich_1978, Bramley_2008} (see
Table~\ref{tbl-thurstone_cases}). This substitution has little impact on
the model's estimation or interpretation, as the Normal and Logistic
distributions share similar statistical properties, differing only by a
scaling factor of approximately \(1.7\)
\citep[pp.~16]{vanderLinden_et_al_2017_I} (see
Figure~\ref{fig-logistic_vs_normal}).

@@

\begin{minipage}{0.50\linewidth}

@@

\includegraphics[width=0.85\linewidth,height=\textheight,keepaspectratio]{./images/figures/density.png}

@@

\end{minipage}%
%
\begin{minipage}{0.50\linewidth}

@@

\includegraphics[width=0.85\linewidth,height=\textheight,keepaspectratio]{./images/figures/cumulative.png}

@@

However, Case V was originally developed to provide a ``rather coarse
scaling'' of traits \citep[pp.~269]{Thurstone_1927b}, prioritizing
statistical simplicity over precision in trait measurement
\citep[pp.~677]{Kelly_et_al_2022}. As a result, its assumptions may not
be suitable for applications beyond the psycho-physical contexts for
which it was created. Thurstone himself cautioned that its use ``should
not be made without (an) experimental test''
\citep[pp.~270]{Thurstone_1927b}, acknowledging that some assumptions
could prove problematic in the presence of complex traits or
heterogeneous stimuli, such as handwriting or English compositions
\citep[pp.~374]{Thurstone_1927a}. Consequently, given that modern CJ
applications frequently involve these types of traits and stimuli, two
main assumptions of Case V may not consistently hold in theory or
practice: the zero correlation and equal dispersion between stimuli.

The assumption of \emph{zero correlation between stimuli} can be better
understood through an example. For instance, when using pairwise
comparisons to evaluate text quality, the assumption implies that a
judge's perception of a trait in one text does not influence his
perception of the same trait in another text. Thurstone attributed this
independence to the cancellation of potential judges' biases, driven by
two opposing and equally weighted effects occurring during the pairwise
comparisons \citep[pp.~268]{Thurstone_1927b}. This cancellation was
mathematically demonstrated by \citet{Andrich_1978}, using the BTL model
under the assumption of discriminal processes with additive biases.
However, it is easy to imagine at least two scenarios where the zero
correlation assumption almost certainly does not hold: when the pairwise
comparison involves multidimensional, complex traits with heterogeneous
stimuli, and when an additional hierarchical structure is relevant to
the stimuli.

In the first scenario, the intricate aspects of multidimensional,
complex traits may introduce dependencies between heterogeneous stimuli
due to certain judges' biases that resist cancellation. Research on text
quality indicates that when judges evaluate such traits, they often rely
on various intricate aspects of the stimuli to form their judgments
\citep{vanDaal_et_al_2016, Lesterhuis_2018, Chambers_et_al_2022}. In
this context, it is not inconceivable that these aspects, being neither
equally weighted nor opposing, may unevenly influence judges'
perceptions, resulting in biases that resist cancellation. For example,
this could occur when a judge assessing the argumentative quality of a
text places disproportionate emphasis on grammatical accuracy,
ultimately favoring texts with fewer errors but weaker arguments. While
direct evidence for this specific scenario is lacking, studies such as
\citet{Pollitt_et_al_2003} demonstrate the presence of judges' biases,
supporting the idea that the factors influencing pairwise comparisons
may not always cancel out.

In the second scenario, the shared context or inherent connections
created by the additional hierarchical structure may introduce
dependencies between stimuli, a statistical phenomenon commonly known as
clustering \citep{Everitt_et_al_2010}. Nevertheless, despite recognizing
such hierarchical structures in CJ data, the statistical handling of
this extra source of dependency in the CJ literature has been
inadequate. For instance, in cases where the CJ data included multiple
samples of stimuli from the same individuals, researchers have often
relied on (averaged) estimated BTL scores to conduct subsequent analyses
and tests at the individual hierarchical level
\citep{Bramley_et_al_2019, Boonen_et_al_2020, Bouwer_et_al_2023, vanDaal_et_al_2017, Jones_et_al_2019, Gijsen_et_al_2021}.
This approach, however, has the significant limitation of ignoring the
uncertainty associated with the BTL scores (refer to section
Section~\ref{sec-theory-issue2} for a detailed discussion of this
issue).

In contrast, the assumption of \emph{equal dispersion between stimuli}
suggests that the variability in the perceived trait level of the
stimulus is the same across all stimuli. While Thurstone acknowledged
that this assumption may be violated when ``dealing with less
conspicuous attributes or with less homogeneous stimuli''
\citep[pp.~374]{Thurstone_1927a}, no study explicitly proposes that this
assumption could also be violated due to the presence of an additional
hierarchical (grouping) structure relevant to the texts. One such
scenario might arise, for example, when comparing texts produced by
university and secondary school students. In this case, university
students may consistently (or more precisely) produce higher-quality
texts, while secondary school students, who exhibit a broader range of
writing abilities, would show greater variability in the quality of
their texts. Although this example is somewhat contrived, it effectively
illustrates how assuming equal dispersions across texts can overlook
meaningful differences in the reliability of text quality across groups
or individuals.

{``However'' paragraph}

{``to mitigate'' paragraph}

@@

Researchers then typically use the estimated BTL scores, or their
transformations, to conduct additional analyses and tests, or to make
decisions regarding the exclusion of certain data in these analyses and
tests. The literature shows that these scores have been employed to
calculate correlations with other assessment methods
\citep{Goossens_et_al_2018, Bouwer_et_al_2023} or to test hypotheses
related to the underlying traits of interest
\citep{Bramley_et_al_2019, Boonen_et_al_2020, Bouwer_et_al_2023, vanDaal_et_al_2017, Jones_et_al_2019, Gijsen_et_al_2021}.
Additionally, the BTL scores have been used to detect biases in judges'
ratings \citep{Pollitt_et_al_2003, Pollitt_2012b}, as well as to
identify ``misfit'' judges and stimuli
\citep{Pollitt_2012b, vanDaal_et_al_2017, Goossens_et_al_2018}, with
considerations for their possible exclusion.

However, the statistical literature advises caution when using estimated
scores for additional analyses and tests, as well as when eliminating
data through ad hoc univariate procedures. A key consideration is that
BTL scores are parameter estimates that inherently carry uncertainty.
Ignoring this uncertainty can bias the analysis and reduce the precision
of hypothesis tests. Notably, the direction and magnitude of such biases
are often unpredictable. Results may be attenuated, exaggerated, or
remain unaffected depending on the degree of uncertainty in the scores
and the actual effects being tested
\citetext{\citealp[pp.~25]{Kline_et_al_2023}; \citealp[pp.~137]{Hoyle_et_al_2023}}.
Moreover, excluding data using ad hoc univariate procedures can compound
these issues by discarding potentially valuable information, further
exacerbating the bias \citep{Zimmerman_1994, McElreath_2020}. Finally,
the reduced precision in hypothesis tests diminishes their statistical
power, increasing the likelihood of committing type-I or type-II errors
\citep{McElreath_2020}.

@@

\subsection{The diverse assessment design features and their role on
reliability and validity}\label{sec-theory-issue3}

@@

\section{Appendix}\label{sec-appendix}

>>>>

Nevertheless, despite the increasing number of CJ studies, unsystematic
and fragmented research approaches have left several critical issues
unaddressed. The present study primarily focuses on two: the
over-reliance on the assumptions of Thurstone's Case V in the
statistical analysis of CJ data, and the apparent disconnect between
CJ's trait measurement and hypothesis testing. The following sections
begin with a brief overview of Thurstone's theory and a detailed
discussion of these issues. Subsequently, the study introduces a
theoretical model for CJ that builds upon Thurstone's theory, alongside
its statistical translation, designed to address the two concerns
simultaneously.

@@

In its most general form, Thurstone's theory deals with pairwise
comparisons of stimuli made by a single judge
\citep[pp.~267]{Thurstone_1927b}. The theory proposes that two key
factors determine the dichotomous outcome of these designs: the
discriminal process of each stimulus and their discriminal difference.
The \emph{discriminal process} represents the psychological impact each
stimulus has on judges or, more simply, their underlying perception of
the stimulus' trait level. According to the theory, the discriminal
process for each stimulus follows a Normal distribution, where its mode
(or mean), referred to as the \emph{modal discriminal process},
indicates the stimulus' position on the trait continuum, and its
dispersion, known as the \emph{discriminal dispersion}, reflects the
variability in the perceived trait level of the stimulus.

For instance, Figure~\ref{fig-discriminal_process} illustrates the
discriminal process distributions along a quality trait continuum for
two written texts. The figure shows that these processes follow a Normal
distribution. Moreover, it depicts differences in the texts' positions
along the quality trait continuum, where text B is positioned two units
further along the continuum than text A, as indicated by their modal
discriminal processes (\(S_{B}=2\) and \(S_{A}=0\)). Finally, it
highlights differences in the texts' discriminal dispersions
(\(\sigma_{B}=1\) and \(\sigma_{A}=0.5\)), showing that text B exhibits
a greater variability in its perceived quality than text A, as reflected
by its wider distribution.

@@

@@

\includegraphics[width=0.7\linewidth,height=\textheight,keepaspectratio]{./images/figures/discriminal_process.png}

@@

\caption{\label{fig-discriminal_process}Example distributions of the
discriminal processes for two written texts}

However, because the discriminal process of a single stimulus is not
directly observable, the theory introduces the \emph{law of comparative
judgment}. This law posits that in pairwise comparisons, a judge
perceives the stimulus positioned further along the trait continuum as
having a higher level of that trait. This principle highlights that the
outcome of a pairwise comparison likely depends on the relative distance
between stimuli rather than their absolute positions on the trait
continuum.

Thus, the theory assumes that the observed dichotomous outcome arises
from the distribution of the difference between the underlying
discriminal processes of the stimuli, known as the \emph{discriminal
difference}. Since the individual discriminal processes follow a Normal
distribution, their difference also follows a Normal distribution. The
mode (or mean) of this distribution, representing the (average) relative
separation, is given by the difference between the modal discriminal
processes of the stimuli \(S_{BA} = S_{B} - S_{A}\). Meanwhile, the
dispersion of the distribution, reflecting the variability in the
relative separation, is calculated as
\(\sigma_{BA} = \sqrt{\sigma_{B}^{2} + \sigma_{A}^{2} - \rho\sigma_{B}\sigma_{A}}\).
Here, \(\sigma_{B}\) and \(\sigma_{A}\) are the previously defined
discriminal dispersions, while \(\rho\) measures the correlation between
their discriminal processes. This correlation quantifies how much the
judge's perception of the trait in one stimulus influences his
perception of the same trait in the other.

Figure~\ref{fig-discriminal_difference} shows the distribution of the
discriminal difference for the texts depicted in
Figure~\ref{fig-discriminal_process}, assuming a correlation of
\(\rho = 0.6\). The figure reveals that, under these conditions, the
judge perceives text B as having significantly higher quality than text
A, as indicated by the shaded gray area under the curve \(P(B > A)\). As
a result, the dichotomous outcome of this comparison almost certainly
favors text B over text A.

@@

\includegraphics[width=0.7\linewidth,height=\textheight,keepaspectratio]{./images/figures/discriminal_difference.png}

@@

\caption{\label{fig-discriminal_difference}Example distribution of the
discriminal difference for the two texts shown in
Figure~\ref{fig-discriminal_process}, assuming a correlation of 0.6}

@@

Additionally, Figure~\ref{fig-correlation} illustrates how varying
correlations influence the distribution of the discriminal difference
for the same two texts. The figure shows that as the correlation
increases, indicating a stronger influence of the judge's perception of
quality in one text on his perception of the other, the distribution of
the discriminal difference becomes narrower. This narrowing affects the
area under the curve that determines the comparison outcome and,
ultimately, the conclusions drawn from this outcome.

For instance, when two texts clearly differ in quality, as depicted in
Figure~\ref{fig-discriminal_process}, higher correlations increase the
likelihood that the discriminal difference more distinctly favors text B
over text A, as indicated by the shaded gray area under the curve in
Figure~\ref{fig-correlation}. Conversely, it is easy to infer that when
the two texts have similar or identical quality levels, higher
correlations reduce the likelihood that the discriminal difference
distinctly favors one text over the other, as the distribution narrows
around zero (not depicted in the figure).

\includegraphics[width=0.7\linewidth,height=\textheight,keepaspectratio]{./images/figures/correlation.png}

\caption{\label{fig-correlation}The effect of correlation on the
distribution of the discriminal difference of the same two written text}

The previous section outlines the general form of Thurstone's theory,
which applies to a CJ design where a single judge evaluates multiple
stimuli. For the practical application of the theory, Thurstone
developed four additional cases derived from this general form, where
each successive case incorporates additional simplifying assumptions.
Case I represents the general form of the theory. Case II extends this
by allowing multiple judges to make comparisons rather than restricting
the comparisons to a single judge. Case III introduces the assumption of
zero correlation between stimuli. Case IV builds on this by assuming
that the stimuli have similar dispersions. Finally, Case V replaces this
assumption with the condition that the stimuli have equal discriminal
dispersions. Table~\ref{tbl-thurstone_cases} summarizes these cases and
their assumptions. For a detailed discussion of this progression, refer
to \citet{Thurstone_1927b} and \citet[pp.~248-253]{Bramley_2008}.

@@

Despite its reliance on the largest number of simplifying assumptions
\citetext{\citealp[pp.~253]{Bramley_2008}; \citealp[pp.~677]{Kelly_et_al_2022}},
Case V remains the most widely used case in the CJ literature. This
popularity stems mainly from its simplified statistical representation
in the Bradley-Terry-Luce (BTL) model
\citep{Bradley_et_al_1952, Luce_1959}. The BTL model mirrors the
assumptions of Case V, with one key difference: while Case V assumes a
Normal distribution for the discriminal processes of the stimuli, the
BTL model uses the more mathematically tractable Logistic distribution
\citep[pp.~254]{Andrich_1978, Bramley_2008} (see
Table~\ref{tbl-thurstone_cases}). This substitution has little impact on
the model's estimation or interpretation, as the Normal and Logistic
distributions share similar statistical properties, differing only by a
scaling factor of approximately \(1.7\)
\citep[pp.~16]{vanderLinden_et_al_2017_I} (see
Figure~\ref{fig-logistic_vs_normal}).

@@

\begin{minipage}{\linewidth}

@@

\includegraphics[width=0.7\linewidth,height=\textheight,keepaspectratio]{./images/figures/density.png}

@@

\end{minipage}%
\newline
\begin{minipage}{\linewidth}

@@

\includegraphics[width=0.7\linewidth,height=\textheight,keepaspectratio]{./images/figures/cummulative.png}

@@

However, Thurstone originally developed Case V to provide a ``rather
coarse scaling'' of traits \citep[pp.~269]{Thurstone_1927b},
prioritizing statistical simplicity over precision in trait measurement
\citep[pp.~677]{Kelly_et_al_2022}. As a result, its assumptions may not
be suitable for applications beyond the psycho-physical contexts for
which it was created. Thurstone himself cautioned that its use ``should
not be made without (an) experimental test''
\citep[pp.~270]{Thurstone_1927b}, acknowledging that some assumptions
could prove problematic in the presence of complex traits or
heterogeneous stimuli, such as handwriting or English compositions
\citep[pp.~374]{Thurstone_1927a}. Consequently, given that modern CJ
applications frequently involve these traits and stimuli, two main
assumptions of Case V may not consistently hold in theory or practice:
the zero correlation and equal dispersion between stimuli.

As outlined in the previous section, the assumption of \emph{zero
correlation between stimuli} suggests that during a pairwise comparison,
a judge's perception of quality in one text does not influence his
perception of the same trait in another text (see
Figure~\ref{fig-correlation}, \(\rho=0\)). Thurstone attributed this
independence to the cancellation of potential judges' biases, driven by
two opposing and equally weighted effects occurring during the pairwise
comparisons \citep[pp.~268]{Thurstone_1927b}. \citet{Andrich_1978}
mathematically demonstrated this cancellation using the BTL model under
the assumption of discriminal processes with additive biases. However,
it is easy to imagine at least two scenarios where the zero correlation
assumption almost certainly does not hold: when the pairwise comparison
involves multidimensional, complex traits with heterogeneous stimuli and
when an additional hierarchical structure is relevant to the stimuli.

In the first scenario, the intricate aspects of multidimensional,
complex traits may introduce dependencies between heterogeneous stimuli
due to certain judges' biases that resist cancellation. Research on text
quality indicates that when judges evaluate these traits, they often
rely on various intricate aspects of the stimuli to form their judgments
\citep{vanDaal_et_al_2016, Lesterhuis_2018, Chambers_et_al_2022}. These
aspects, which are likely neither equally weighted nor opposing, may
influence judges' perceptions unevenly. For example, this could occur
when a judge assessing the argumentative quality of a text places
disproportionate emphasis on grammatical accuracy, ultimately favoring
texts with fewer errors but weaker arguments. Ignoring these relevant
additional ``traits'' can result in biases that resist cancellation,
introducing dependencies between stimuli
\citep[pp.~346]{vanderLinden_et_al_2017_II} and ultimately violating the
assumption of zero correlation. While direct evidence for the specific
mechanisms causing biases is lacking, studies such as
\citet{Pollitt_et_al_2003} demonstrate the presence of such biases,
supporting the idea that the factors influencing pairwise comparisons
may not always cancel out.

In the second scenario, the shared context or inherent connections
created by additional hierarchical structures may introduce dependencies
between stimuli, a statistical phenomenon commonly known as clustering
\citep{Everitt_et_al_2010}. Although the CJ literature acknowledges the
presence of such hierarchical structures in CJ data, the statistical
handling of this extra source of dependency has been inadequate. For
example, when CJ data includes multiple samples of stimuli from the same
individuals, researchers often rely on (average) estimated BTL scores to
conduct subsequent analyses and tests at the individual hierarchical
level
\citep{Bramley_et_al_2019, Boonen_et_al_2020, Bouwer_et_al_2023, vanDaal_et_al_2017, Jones_et_al_2019, Gijsen_et_al_2021}.
This approach, however, has the significant limitation of ignoring the
uncertainty associated with the BTL scores, which generates additional
statistical and measurement issues, as discussed in section
Section~\ref{sec-theory-issue2}.

In any case, the psychometric and statistical literature strongly
advises against ignoring relevant additional traits or overlooking
clustering (grouping) structures that may introduce dependencies between
stimuli. First, ignoring additional aspects pertinent to the trait of
interest can cause a dimensional mismatch, which can lead to an
overestimation of the precision (reliability) of the trait's measurement
\citep[pp.~340-341]{Hoyle_et_al_2023} or, worse, introduce bias into the
measurement process \citep{Ackerman_1989}. Additionally, overlooking
relevant hierarchical (or grouping) structures can exacerbate the
inflation of reliability by reducing the accuracy of the model's
parameters \citep[pp.~482]{Hoyle_et_al_2023}. Taken together, these
oversights undermine the reliability of the measurement process and,
since validity cannot exist without reliability
\citep[pp.~2]{Perron_et_al_2015}, ultimately compromise the validity of
the results derived from it.

@@

Researchers then typically use the estimated BTL scores, or their
transformations, to conduct additional analyses or hypothesis tests. For
example, these scores have been used to identify `misfit' judges and
stimuli \citep{Pollitt_2012b, vanDaal_et_al_2017, Goossens_et_al_2018},
detect biases in judges' ratings
\citep{Pollitt_et_al_2003, Pollitt_2012b}, calculate correlations with
other assessment methods \citep{Goossens_et_al_2018, Bouwer_et_al_2023},
or test hypotheses related to the underlying trait of interest
\citep{Bramley_et_al_2019, Boonen_et_al_2020, Bouwer_et_al_2023, vanDaal_et_al_2017, Jones_et_al_2019, Gijsen_et_al_2021}.

However, the statistical literature advises caution when using estimated
scores for additional analyses and tests. A key consideration is that
BTL scores are parameter estimates that inherently carry uncertainty.
Ignoring this uncertainty can bias the analysis and reduce the precision
of hypothesis tests. Notably, the direction and magnitude of such biases
are often unpredictable. Results may be attenuated, exaggerated, or
remain unaffected depending on the degree of uncertainty in the scores
and the actual effects being tested
\citetext{\citealp[pp.~25]{Kline_et_al_2023}; \citealp[pp.~137]{Hoyle_et_al_2023}}.
Finally, the reduced precision in hypothesis tests diminishes their
statistical power, increasing the likelihood of committing type-I or
type-II errors \citep{McElreath_2020}.

@@

@@
